---
title: "DABN_case2_data"
output: html_document
date: '2023-02-06'
---


```{r}
knitr::opts_chunk$set(echo = TRUE)
```

Ideas:
    - Check the profit margins of other similar companies (allabolag?)
    - Box plot modeling minutes to time to capture hotspots throughout the day
        - Maybe facet by weekday?
    - Box plot modeling time of day to weekday
    - Incorporate search data from Google?
    - Prescriptive Ideas
        - Need to build data analytics as service first
    - Research market of firm
        - Who are the factors/suppliers and the consumers?
            - How do actions from the supplier side impact the ticket sales?
            - How do actions/cultural movements affect ticket sales from consumer side?
    - Can we estimate the average amount of time a search result is still relevant?
        - We can minimize transaction costs by caching older search results
        - Perhaps it varies with start/end locations? Or varies by density of searches?
    - Calculate a ratio of Searches-to-Purchases
        - How does this ratio change over the course of the day? Week? Month (if given enough data)?
        
    - Adjust currency pricing (to SEK?)
     
    

```{r}
# you may need to dowload the following package:
# install.packages("tidyjson")

library(tidyverse)
library(tidyjson)
library(lubridate)

# change to correct path, note the "/" instead of  "\"
path <- "C:/Users/danny/Desktop/Coding stuff/Lund University/DABN17/Case2"

orders_list <- vector(mode = 'list', length = 0)
for(i in 0:2){
    orders_list[[paste('split_',i,sep="")]] <- readLines(paste(path, "/aob_data/aob_data/orders.split-",i,".json", sep="")) %>% #ADJUST n BEFORE RUNNING
        spread_all() %>% 
        tibble() %>% 
        select(!c(1:4), !c("..JSON"))
}

meta_click_list <- vector(mode = 'list', length = 24)
for(i in 0:23){
    meta_click_list[[paste('split_',i,sep="")]] <- readLines(paste(path, "/aob_data/aob_data/meta_clicks.split-",i,".json", sep="")) %>% #ADJUST n BEFORE RUNNING
        spread_all() %>% 
        tibble() %>% 
        # "Unpack" the json files and remove variables that carry no useful information to us, 
        # i.e columns 1-4 (see the files for information regarding the variables):
            # document id   - (one value for each observation)
            # index         - (what data it refer to)
            # id            - (not the id-variable we are interested in)
            # score         - (1 for all datapoints)
        select(!c(1:4), !c("..JSON"))
}

# bind together data of the same category
orders <- bind_rows(orders_list) %>% # bind together data of the same category
    rename_with(~sub("_source.", "", .x)) %>% # rename columns by removing leading "_source."
    arrange(search_id) %>% # re-order by search_id
    distinct(search_id, .keep_all = T) # remove duplicates

clicks <- bind_rows(meta_click_list) %>% # bind together data of the same category
    rename_with(~sub("_source.", "", .x)) %>% # rename columns by removing leading "_source."
    arrange(search_id) %>% # re-order by search_id
    distinct(search_id, .keep_all = T) # remove duplicates

# merge on search id to get dataset of which clicks resulted in an order
click_order_join <- left_join(clicks, orders, by = "search_id")
order_click_join <- left_join(orders, clicks, by = "search_id")

#remove dataframes we don't use anymore
rm(orders_list, meta_click_list)
```

```{r}
View(clicks[1:50,])
View(orders[1:50,])

View(click_order_join[1:50,])
```

```{r}
clicks_updated <- clicks %>% 
    mutate(created_at_datetime = as_datetime(created_at),
           created_at_date = as_date(created_at),
           created_at_wday = factor(wday(created_at_date), labels = c('S', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
           created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
           created_at_hour = hour(created_at_datetime),
           # created_at_min = minute(created_at_datetime))
           created_at_min = factor(as.numeric(strftime(created_at_datetime, format="%M")) %/% 15, labels = c("0-15","15-30","30-45","45-60"))) %>% 
    filter(created_at_date < "2023-01-30")

click_order_join_upd <- click_order_join %>% 
    mutate(created_at_datetime = as_datetime(created_at.x),
           created_at_date = as_date(created_at.x),
           created_at_wday = factor(wday(created_at_date), labels = c('S', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
           created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
           created_at_hour = hour(created_at_datetime),
           # created_at_min = minute(created_at_datetime))
           created_at_min = factor(as.numeric(strftime(created_at_datetime, format="%M")) %/% 15, 
                                   labels = c("0-15","15-30","30-45","45-60"))) %>% 
    filter(created_at_date < "2023-01-30")

click_order_pivot <- click_order_join %>% 
    mutate(created_at_datetime = as_datetime(created_at.x),
           created_at_date = as_date(created_at.x),
           created_at_wday = factor(wday(created_at_date), labels = c('S', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
           created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
           created_at_hour = hour(created_at_datetime),
           # created_at_min = minute(created_at_datetime))
           created_at_min = factor(as.numeric(strftime(created_at_datetime, format="%M")) %/% 15, 
                                   labels = c("0-15","15-30","30-45","45-60"))) %>% 
    filter(created_at_date < "2023-01-30") %>% 
    pivot_longer(cols = c(result_set_cheapest_price, result_set_fastest_price, result_set_best_price),
                names_to = "ticket_option", values_to = "ticket_option_price") %>% 
    mutate(ticket_match = (itinerary_sales_price == ticket_option_price)) %>% 
    filter(ticket_match == TRUE)

# order_click_join_upd <- order_click_join %>% 
#     mutate(created_at_datetime = as_datetime(created_at_date),
#            created_at_date = as_date(created_at_date),
#            created_at_wday = factor(wday(created_at_date), labels = c('S', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
#            created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
#            created_at_hour = hour(created_at_datetime),
#            # created_at_min = minute(created_at_datetime))
#            created_at_min = factor(as.numeric(strftime(created_at_datetime, format="%M")) %/% 15, 
#                                    labels = c("0-15","15-30","30-45","45-60"))) %>% 
#     filter(created_at_date < "2023-01-30")

View(click_order_pivot[1:50,])
View(click_order_join_upd[1:50,])
# View(order_click_join_upd[1:50,])
```

```{r}
clicks_updated %>% 
    ggplot(aes(x = created_at_wday, y = created_at_time)) +
    geom_bin2d() +
    theme_minimal()

clicks_updated %>% 
    ggplot(aes(x = created_at_hour)) +
    geom_bar(position = "dodge") +
    facet_grid(~created_at_wday) +
    theme_linedraw() +
    labs(x = "Hour", y = "Count", title = "Bar Plot of Clicks by Hour", subtitle = "Faceted on Weekday Groupings") +
    scale_x_continuous(limits = c(0, 24), breaks = round(seq(0,23, length.out=24)),1) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, size = 7.5))

clicks_updated %>% 
    ggplot(aes(x = created_at_hour)) +
    geom_bar(position = "dodge") +
    theme_linedraw() +
    labs(x = "Hour", y = "Count", title = "Bar Plot of Clicks by Hour")

clicks_updated %>% 
    ggplot(aes(x = created_at_wday)) +
    geom_bar(position = "dodge") +
    theme_linedraw() +
    labs(x = "Hour", y = "Count", title = "Bar Plot of Clicks by Weekday")

clicks_updated %>% 
    ggplot(aes(x = created_at_date)) +
    geom_bar(position = "dodge") +
    theme_linedraw() +
    labs(x = "Date", y = "Count", title = "Bar Plot of Clicks by Over Time")
```

```{r}
click_order_join_upd %>% 
    filter(paid %in% c(F,T),
           itinerary_with_baggage %in% c(F,T)) %>% 
    ggplot(aes(x = created_at_date, fill = paid)) +
    geom_bar(position = "fill") +
    theme_linedraw() +
    labs(x = "Date", y = "Count", title = "Bar Plot of Purchased Tickets by Over Time", subtitle = "Faceted on whether baggage was included") +
    facet_grid(~itinerary_with_baggage)

click_order_join_upd %>% 
    filter(paid %in% c(F,T),
           itinerary_with_baggage %in% c(F,T)) %>% 
    ggplot(aes(x = created_at_date, fill = paid)) +
    geom_bar(position = "dodge") +
    theme_linedraw() +
    labs(x = "Date", y = "Count", title = "Bar Plot of Purchased Tickets by Over Time", subtitle = "Faceted on whether baggage was included") +
    facet_grid(~itinerary_with_baggage)
```

```{r}
click_order_join_upd %>% 
    filter(paid %in% c(F,T),
           is.na(itinerary_travel_time) != T) %>% 
    mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
    filter(itinerary_travel_time <= 15) %>% 
    ggplot(aes(x = itinerary_travel_time, fill = paid)) +
    geom_bar() +
    scale_x_binned(n.breaks = 16) +
    labs(x = "Hours", y = "Count") +
    theme_linedraw()

click_order_join_upd %>% 
    filter(paid %in% c(F,T),
           is.na(itinerary_travel_time) != T) %>% 
    mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
    filter(itinerary_travel_time <= 15) %>% 
    ggplot(aes(x = itinerary_travel_time, fill = paid)) +
    geom_bar(position = "fill") +
    scale_x_binned(n.breaks = 16) +
    labs(x = "Hours", y = "Count") +
    theme_linedraw() +
    scale_y_continuous(breaks = seq(0, 1, length.out=11))

click_order_join_upd %>% 
    filter(paid %in% c(F,T),
           is.na(itinerary_travel_time) != T) %>% 
    mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
    filter(itinerary_travel_time > 15) %>% 
    ggplot(aes(x = itinerary_travel_time, fill = paid)) +
    geom_bar() +
    scale_x_binned(n.breaks = 16) +
    labs(x = "Hours", y = "Count") +
    theme_linedraw()

click_order_join_upd %>% 
    filter(paid %in% c(F,T),
           is.na(itinerary_travel_time) != T) %>% 
    mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
    filter(itinerary_travel_time > 15) %>% 
    ggplot(aes(x = itinerary_travel_time, fill = paid)) +
    geom_bar(position = "fill") +
    scale_x_binned(n.breaks = 16) +
    labs(x = "Hours", y = "Count") +
    theme_linedraw() +
    scale_y_continuous(breaks = seq(0, 1, length.out=11))
```

```{r}
click_order_pivot %>% 
    ggplot(aes(ticket_option)) +
    geom_bar()
```

