---
title: "DABN_case2_data"
output: html_document
date: '2023-02-06'
---


```{r}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 16,
                      fig.height = 9)
```

Ideas:
    - Check the profit margins of other similar companies (allabolag?)
    - Box plot modeling minutes to time to capture hotspots throughout the day
        - Maybe facet by weekday?
    - Box plot modeling time of day to weekday
    - Incorporate search data from Google?
    - Prescriptive Ideas
        - Need to build data analytics as service first
    - Research market of firm
        - Who are the factors/suppliers and the consumers?
            - How do actions from the supplier side impact the ticket sales?
            - How do actions/cultural movements affect ticket sales from consumer side?
    - Can we estimate the average amount of time a search result is still relevant?
        - We can minimize transaction costs by caching older search results
        - Perhaps it varies with start/end locations? Or varies by density of searches?
    - Calculate a ratio of Searches-to-Purchases
        - How does this ratio change over the course of the day? Week? Month (if given enough data)?
        
    - Adjust currency pricing (to SEK?)
     
    

```{r}
# you may need to dowload the following package:
# install.packages("tidyjson")
library(tidyverse)
# library(tidyjson)
library(lubridate)

# change to correct path, note the "/" instead of  "\"
# path <- "C:/Users/danny/Desktop/Coding stuff/Lund University/DABN17/Case2"
```

```{r}
# orders_list <- vector(mode = 'list', length = 0)
# for(i in 0:2){
#     orders_list[[paste('split_',i,sep="")]] <- readLines(paste(path, "/aob_data/aob_data/orders.split-",i,".json", sep="")) %>% #ADJUST n BEFORE RUNNING
#         spread_all() %>% 
#         tibble() %>% 
#         select(!c(1:4), !contains("JSON"))
# }
# 
# meta_click_list <- vector(mode = 'list', length = 24)
# for(i in 0:23){
#     meta_click_list[[paste('split_',i,sep="")]] <- readLines(paste(path, "/aob_data/aob_data/meta_clicks.split-",i,".json", sep="")) %>% #ADJUST n BEFORE RUNNING
#         spread_all() %>% 
#         tibble() %>% 
#         # "Unpack" the json files and remove variables that carry no useful information to us, 
#         # i.e columns 1-4 (see the files for information regarding the variables):
#             # document id   - (one value for each observation)
#             # index         - (what data it refer to)
#             # id            - (not the id-variable we are interested in)
#             # score         - (1 for all datapoints)
#         select(!c(1:4), !contains("JSON"))
# }
```

```{r}
# # bind together data of the same category
# orders <- bind_rows(orders_list) %>% # bind together data of the same category
#     rename_with(~sub("_source.", "", .x)) %>% # rename columns by removing leading "_source."
#     arrange(search_id) %>% # re-order by search_id
#     distinct(search_id, .keep_all = T) # remove duplicates
# 
# 
# 
# clicks <- bind_rows(meta_click_list) %>% # bind together data of the same category
#     rename_with(~sub("_source.", "", .x)) %>% # rename columns by removing leading "_source."
#     arrange(search_id) %>% # re-order by search_id
#     distinct(search_id, .keep_all = T) # remove duplicates



# merge on search id to get dataset of which clicks resulted in an order
# click_order_join <- left_join(clicks, orders, by = "search_id")
# order_click_join <- left_join(orders, clicks, by = "search_id")

# saveRDS(orders, file="aob_orders.rds")
# saveRDS(clicks, file="aob_clicks.rds")
# saveRDS(click_order_join, file="aob_clicks_order_join.rds")

#remove dataframes we don't use anymore
# rm(orders_list, meta_click_list)
```


```{r}
# View(clicks[1:50,])
# View(orders[1:50,])
# View(click_order_join[1:50,])
```

```{r}
## rates taken from Keshav
# exch.rates <- data.frame(itinerary_currency = c("DKK", "EUR", "NOK", "SEK"), 
#                          exch = c(1.411099, 10.6892, 1.063355, 1))
# currency.df <- clicks_updated %>% count(itinerary_currency) %>% 
#     left_join(exch.rates, 
#               by = "itinerary_currency")

## Cleaning the clicks data
# clicks_updated <- clicks %>% 
#     mutate(created_at_datetime = as_datetime(created_at),
#            created_at_date = as_date(created_at),
#            created_at_wday = factor(wday(created_at_date), labels = c('Su', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
#            created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
#            created_at_hour = hour(created_at_datetime)) %>% 
#     filter(!is.na(itinerary_currency)) %>% rowwise() %>% # Here we remove lines of data that do not have any price data.
#     mutate(across(.cols = contains("_price"), # The following code changes the currency rates
#                   .fns = ~ case_when(itinerary_currency == "SEK" ~ .*1,
#                                      itinerary_currency == "DKK" ~ .*1.411099,
#                                      itinerary_currency == "EUR" ~ .*10.6892,
#                                      itinerary_currency == "NOK" ~ .*1.063355,
#                                      TRUE ~ NA_real_)))
# saveRDS(clicks_updated, file="aob_clicks_updated.rds")

# ## Cleaning the merged/joined data
# click_order_join_upd <- click_order_join %>% 
#     mutate(created_at_datetime = as_datetime(created_at.x),
#            created_at_date = as_date(created_at.x),
#            created_at_wday = factor(wday(created_at_date), 
#                                     labels = c('Su', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
#            created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
#            created_at_hour = hour(created_at_datetime))
           # created_at_min = minute(created_at_datetime))
           # created_at_min = factor(as.numeric(strftime(created_at_datetime, format="%M")) %/% 15, labels = c("0-15","15-30","30-45","45-60"))) %>% 
    # filter(created_at_date < "2023-01-30")

# click_order_pivot <- click_order_join %>%
#     mutate(created_at_datetime = as_datetime(created_at.x),
#            created_at_date = as_date(created_at.x),
#            created_at_wday = factor(wday(created_at_date),
#                                     labels = c('S', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
#            created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
#            created_at_hour = hour(created_at_datetime),
#            # created_at_min = minute(created_at_datetime))
#            created_at_min = factor(as.numeric(strftime(created_at_datetime, format="%M")) %/% 15,
#                                    labels = c("0-15","15-30","30-45","45-60"))) %>%
#     filter(created_at_date < "2023-01-30") %>%
#     pivot_longer(cols = c(result_set_cheapest_price,
#                           result_set_fastest_price, 
#                           result_set_best_price),
#                 names_to = "ticket_option", values_to = "ticket_option_price") %>%
#     mutate(ticket_match = (itinerary_sales_price == ticket_option_price)) %>%
#     filter(ticket_match == TRUE)

# order_click_join_upd <- order_click_join %>% 
#     mutate(created_at_datetime = as_datetime(created_at_date),
#            created_at_date = as_date(created_at_date),
#            created_at_wday = factor(wday(created_at_date), labels = c('S', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
#            created_at_time = hour(created_at_datetime) + minute(created_at_datetime)/60,
#            created_at_hour = hour(created_at_datetime),
#            # created_at_min = minute(created_at_datetime))
#            created_at_min = factor(as.numeric(strftime(created_at_datetime, format="%M")) %/% 15, 
#                                    labels = c("0-15","15-30","30-45","45-60"))) %>% 
#     filter(created_at_date < "2023-01-30")

# View(clicks_updated[1:50,])
# View(click_order_join_upd[1:50,])
# View(order_click_join_upd[1:50,])
```

```{r load_SavedData}
orders <- readRDS("aob_orders.rds")
clicks_updated <- readRDS("aob_clicks_updated.rds")
click_order_join <- left_join(clicks_updated, orders, by = "search_id") #%>% 
    # mutate(created_at_datetime.x = as_datetime(created_at.x),
    #        created_at_date.x = as_date(created_at.x),
    #        created_at_wday.x = factor(wday(created_at_date.x),
    #                                 labels = c('Su', 'M', 'T', 'W', 'Th', 'F', 'Sa')),
    #        created_at_time.x = hour(created_at_datetime.x) + minute(created_at_datetime.x)/60,
    #        created_at_hour.x = hour(created_at_datetime.x))

View(orders[1:50,])
View(clicks_updated[1:50,])
View(click_order_join[1:50,])
```


```{r}
avg.hr <- clicks_updated %>%
    group_by(created_at_hour, created_at_wday, created_at_date) %>%
    summarise(n=n(), .groups = "keep") %>% ungroup(created_at_date) %>% 
    summarise(mean = mean(n), .groups = "keep") %>% 
    ggplot(aes(x = created_at_hour, y=mean, col=created_at_wday)) +
    geom_line(size=1) +
    theme_linedraw() +
    labs(x = "Hour", y = "Count",
         title = "Average Clicks per Hour") +
    scale_x_continuous(breaks = seq(0,23, length.out=24), minor_breaks = NULL) +
    scale_color_brewer(palette = "Set1", name = "Weekday") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

avg.hr.mb <- clicks_updated %>%
    filter(created_at_date < "2023-01-30") %>%
    group_by(created_at_hour, mobile) %>%
    summarise(Count = n(), .groups = "keep") %>%
    ggplot(aes(x = created_at_hour, y=Count, col=mobile)) +
    geom_line(size=1) +
    theme_linedraw() +
    labs(x = "Hour", y = "Count",
         title = "Total Clicks per Hour") +
    scale_x_continuous(breaks = seq(0,23, length.out=24), minor_breaks = NULL) +
    scale_y_continuous(labels = scales::comma) +
    scale_color_brewer(palette = "Set1", name = "Mobile") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
    # facet_grid(rows = vars(mobile))

# clicks_updated %>%
#     ggplot(aes(x = created_at_hour)) +
#     geom_bar(position = "dodge") +
#     theme_linedraw() +
#     labs(x = "Hour", y = "Count", title = "Bar Plot of Clicks by Hour")

clicks_updated %>%
    filter(created_at_date < "2023-01-30") %>%
    group_by(created_at_hour, created_at_wday, mobile) %>%
    summarise(Count = n(), .groups = "keep") %>%
    ggplot(aes(x = created_at_hour, y=Count, col = created_at_wday)) +
    geom_line(size=1) +
    theme_linedraw() +
    labs(x = "Hour", y = "Count",
         title = "Total Clicks per Hour") +
    scale_x_continuous(breaks = seq(0,23, length.out=24), minor_breaks = NULL) +
    scale_y_continuous(labels = scales::comma) +
    scale_color_brewer(palette = "Set1", name = "Weekday") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    facet_grid(rows = vars(mobile))

loc.clicks <- clicks_updated %>%
    rowwise() %>% 
    mutate(trip.1leg = str_split_fixed(itinerary_string, pattern = ", ", n=2)[1]) %>%
    mutate(trip.start = str_split_fixed(trip.1leg, pattern = "-", n=2)[1]) %>% 
    ungroup() %>% count(trip.start) %>% 
    mutate(trip.start = fct_reorder(trip.start, n, .desc=T)) %>% 
    slice_max(n = 15, order_by = n) %>% 
    ggplot(aes(trip.start, n)) +
    geom_col() +
    scale_y_continuous(labels = scales::comma) +
    theme_linedraw() +
    labs(x = "Starting Airport", y = "Count", 
         title = "Total Clicks by Starting Trip Location")

# clicks_updated %>%
#     filter(created_at_date < "2023-01-30") %>% 
#     ggplot(aes(x = created_at_date, fill = itinerary_currency)) +
#     geom_bar() +
#     theme_linedraw() +
#     labs(x = "Date", y = "Count", title = "Bar Plot of Clicks by Over Time") +
#     scale_x_continuous(breaks = seq(0,23, length.out=24), minor_breaks = NULL) +
#     scale_fill_brewer(palette = "Set1")
```

```{r}
time.paid <- click_order_join %>% 
    filter(paid %in% c(F,T),
           itinerary_with_baggage %in% c(F,T),
           created_at_date.x <= as.Date("2023-01-29")) %>% 
    group_by(created_at_date.x, paid, itinerary_with_baggage) %>% 
    summarise(Count = n(), .groups = "keep") %>% 
    ggplot(aes(x = created_at_date.x, y = Count, col = paid)) +
    geom_line(size = 1) +
    theme_linedraw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    scale_x_date(limits = c(as.Date("2023-01-09"), as.Date("2023-01-29")),
                 date_breaks = "2 days", 
                 labels = function(.x) format(.x, format = "%m-%d")) +
    scale_color_discrete(name = "Orders were \nPaid?") +
    facet_grid(~itinerary_with_baggage) +
    labs(x = "Date", y = "Count", 
         title = "Line Plot of Purchased Tickets Over Time", 
         subtitle = "Faceted on whether baggage was included") 

time.paid.mb <- click_order_join %>% 
    filter(paid %in% c(F,T),
           mobile %in% c(F,T)) %>% 
    group_by(created_at_hour, paid, mobile) %>% 
    summarise(Count = n(), .groups = "keep") %>% 
    ggplot(aes(x = created_at_hour, y = Count, col = paid)) +
    geom_line(size = 1) +
    theme_linedraw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    scale_x_continuous(breaks = seq(0,23, length.out=24), minor_breaks = NULL) +
    scale_color_discrete(name = "Orders were \nPaid?") +
    facet_grid(cols = vars(mobile)) +
    labs(x = "Hour", y = "Count", 
         title = "Line Plot of Purchased Tickets Over Time", 
         subtitle = "Faceted on whether a mobile phone was used") 
```

```{r}
click_order_join %>% 
    filter(paid %in% c(F,T)) %>% 
    group_by(created_at_hour, paid) %>%
    summarise(Count = n(), .groups = "keep") %>% 
    # plot start
    ggplot(aes(x = created_at_hour, y=Count, col=paid)) +
    geom_line(size=1) +
    theme_light() +
    labs(x = "Hour", y = "Count",
         title = "Total Clicks per Hour that Resulted in an Order") +
    scale_x_continuous(breaks = seq(0,23, length.out=24), minor_breaks = NULL) +
    scale_color_brewer(palette = "Set1", name = "Paid?") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=0.5, size = 7.5))
    # ggplot(aes(x = created_at_date, y = Count, col = paid)) +
    # geom_line(size = 1) +
    # theme_linedraw() +
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    # scale_x_date(limits = c(as.Date("2023-01-09"), as.Date("2023-01-29")),
    #              date_breaks = "2 days", 
    #              labels = function(.x) format(.x, format = "%m-%d")) +
    # scale_color_discrete(name = "Orders were \nPaid?") +
    # facet_grid(rows = vars(created_at_wday))
    # labs(x = "Date", y = "Count", 
    #      title = "Bar Plot of Purchased Tickets by Over Time", 
    #      subtitle = "Faceted on whether baggage was included", 
    #      caption = "")
```

```{r}
click_order_join %>% 
    filter(paid %in% c(F,T),
           is.na(itinerary_travel_time) != T) %>% 
    mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
    ggplot(aes(x = itinerary_travel_time, fill = paid)) +
    geom_bar() +
    scale_x_binned(n.breaks = 16) +
    scale_y_continuous(labels = scales::comma) +
    scale_fill_brewer(palette = "Set1") +
    labs(x = "Hours", y = "Count of Orders") +
    theme_classic()

click_order_join %>% 
    filter(paid %in% c(F,T),
           is.na(itinerary_sales_price) != T) %>%
    # group_by(paid, itinerary_sales_price) %>% count(paid) %>%
    ggplot(aes(x = paid, y = itinerary_sales_price)) +
    geom_violin() +
    scale_y_log10(labels = scales::comma) +
    # scale_fill_brewer(palette = "Set1") +
    labs(y = "Itinerary Sales Price (SEK)", x = "Were Orders Paid?") +
    theme_classic()

# click_order_join %>% 
#     filter(paid %in% c(F,T),
#            is.na(itinerary_travel_time) != T) %>% 
#     mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
#     filter(itinerary_travel_time <= 15) %>% 
#     ggplot(aes(x = itinerary_travel_time, fill = paid)) +
#     geom_bar() +
#     scale_x_binned(n.breaks = 16) +
#     labs(x = "Hours", y = "Count") +
#     theme_linedraw()

# click_order_join %>% 
#     filter(paid %in% c(F,T),
#            is.na(itinerary_travel_time) != T) %>% 
#     mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
#     filter(itinerary_travel_time <= 15) %>% 
#     ggplot(aes(x = itinerary_travel_time, fill = paid)) +
#     geom_bar(position = "fill") +
#     scale_x_binned(n.breaks = 16) +
#     labs(x = "Hours", y = "Count") +
#     theme_linedraw() +
#     scale_y_continuous(breaks = seq(0, 1, length.out=11))
# 
# click_order_join %>% 
#     filter(paid %in% c(F,T),
#            is.na(itinerary_travel_time) != T) %>% 
#     mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
#     filter(itinerary_travel_time > 15) %>% 
#     ggplot(aes(x = itinerary_travel_time, fill = paid)) +
#     geom_bar() +
#     scale_x_binned(n.breaks = 16) +
#     labs(x = "Hours", y = "Count") +
#     theme_linedraw()
# 
# click_order_join %>% 
#     filter(paid %in% c(F,T),
#            is.na(itinerary_travel_time) != T) %>% 
#     mutate(itinerary_travel_time = itinerary_travel_time/60) %>% 
#     filter(itinerary_travel_time > 15) %>% 
#     ggplot(aes(x = itinerary_travel_time, fill = paid)) +
#     geom_bar(position = "fill") +
#     scale_x_binned(n.breaks = 16) +
#     labs(x = "Hours", y = "Count") +
#     theme_linedraw() +
#     scale_y_continuous(breaks = seq(0, 1, length.out=11))
```

```{r}
click_order_join %>%
    filter(!is.na(paid),
           !is.na(itinerary_travel_time),
           !is.na(itinerary_direct_flight),
           !is.na(itinerary_with_baggage)) %>%
    # ggplot(aes(x = itinerary_travel_time/60, y = meta_clicked_price, col=paid)) +
    ggplot(aes(x = itinerary_travel_time/60, y = itinerary_sales_price_pax, col = itinerary_direct_flight)) +
    geom_point(alpha = 0.1) +
    geom_density2d() +
    # geom_hex(alpha = 0.25) +
    # geom_smooth(method = "loess") +
    scale_x_log10(label = scales::comma, minor_breaks = NULL) +
    scale_y_log10(label = scales::comma, minor_breaks = NULL) +
    labs(x = "Log of Travel Time (Hours)", y = "Log of Ticket Price (SEK)") +
    facet_grid(rows = vars(itinerary_with_baggage),
               cols = vars(paid))

# click_order_join %>% 
#     rowwise() %>% mutate(paid = if_else(is.na(paid), FALSE, paid)) %>% ungroup() %>% 
#     filter(!is.na(itinerary_travel_time),
#            !is.na(itinerary_direct_flight),
#            !is.na(itinerary_with_baggage)) %>%
#     # ggplot(aes(x = itinerary_travel_time/60, y = meta_clicked_price, col=paid)) +
#     ggplot(aes(x = itinerary_travel_time/60, y = result_set_cheapest_price, col = paid)) +
#     geom_point(alpha = 0.05) +
#     geom_density2d() +
#     # geom_hex(alpha = 0.25) +
#     # geom_smooth(method = "loess") +
#     scale_x_log10(label = scales::comma, minor_breaks = NULL) +
#     scale_y_log10(label = scales::comma, minor_breaks = NULL) +
#     labs(x = "Log of Travel Time (Hours)", y = "Log of Ticket Price (SEK)") +
#     facet_grid(cols = vars(paid))
```

```{r}
total.order.ct <- click_order_join %>% 
    filter(!is.na(paid),
           !is.na(mobile),
           !is.na(itinerary_travel_time),
           !is.na(itinerary_sales_price),
           itinerary_sales_price < 50000) %>% 
    group_by(mobile, paid) %>% summarise(count = n(), .groups = "keep") %>% 
    ggplot(aes(x = mobile, y = count, fill = paid)) +
    geom_col(position = "dodge") +
    scale_y_continuous(labels = scales::comma) +
    scale_fill_brewer(palette = "Set1", name = "Paid") +
    labs(x = "Mobile Search", y = "Count",
         title = "Count of Paid Orders",
         subtitle = "Separated by if the order originated from a mobile click") +
    guides(colour = guide_legend(override.aes = list(alpha = 1))) +
    theme_classic()
```

```{r graph.save}
plotlist <- list(avg.hr, avg.hr.mb, loc.clicks, time.paid, time.paid.mb, total.order.ct)

for(i in 1:6){
    ggsave(plot = plotlist[[i]], filename = paste0("ggplot_",i,".png",sep=""), device = "png")
}

```

